To Do List

### 2018-09-13 ToDo.Rmd
updates

*Make a bullet pointed list for manuscript
*Apply RF, GBM, SVM (later), MLR using our features
*Finish Methods
*Finish running code applied to 100 iterations of undersampling
*Apply pipeline to K562 cell line

>>>>

+ Make a bullet pointed list for manuscript
* Apply RF, GBM, SVM (later), MLR using our features
+ Finish Methods
+ Finish running code applied to 100 iterations of undersampling
* Apply pipeline to K562 cell line

* Should figures be placed in back of paper (in Appendix section)?
* Line 60 of manuscript: Check for accuracy?

* in table with total features put (*) for removed then state why
* Finish results outline
* Finish results manuscript
